Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-03-25 curvature.tex
Some reasonable kappa-access plots.

%---[ figures ]-----------------------------------------------------------------

@@

\begin{document}
\title{Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-prune-regraft Graph}

@@

After the chain has achieved stationarity, one sees a \ldots~\todo{results}.

>>>>

@@

\begin{document}
\title{Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-Prune-Regraft Graph}

@@

\begin{figure}
	\hspace*{\stretch{1}}
	\subfigure[\label{fig:short-time-kappa-access}]{\includegraphics[width=3in]{figs/short-time-kappa-access}}
	\hspace*{\stretch{2}}
	\subfigure[\label{fig:long-time-kappa-access}]{\includegraphics[width=3in]{figs/long-time-kappa-access}}
	\hspace*{\stretch{1}}
    \caption{Access times for degree 24 trees and $\kappa$.}
	\label{fig:kappa-access}
\end{figure}
